Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross-Sections using a DD Neutron Generator for Medical Isotope Studies

### 2017-02-28 First_np_Paper/first_np_paper.tex
Updated section 3 with Lee edits

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Results of cross section measurement. Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
\label{tab:xs_results}
\begin{tabular}{@{}cc@{}}
\toprule
Reaction                                                                            & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                       \\ \midrule
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
\end{tabular}
\end{table}

@@

The results for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections can also be seen plotted in Figures \ref{fig:sc_xs} and \ref{fig:cu_xs}, respectively. It is apparent that the relative cross sections measured in the present work are consistent with both the small quantity of other literature results, and are measured to within 6\% uncertainty, lower than existing measurements. In addition, the results presented in this work show strong agreement with the recommended values from both the ENDF/B-VII.1 nuclear data library and reaction modeling results from TALYS\cite{koning2005talys}.

\comment{Waiting on Lee for EMPIRE, ALICE data and language discussing differences and the significance of this.}

\comment{Mention Shimizu data specifically? }

\comment{Add a zoomed-in view like in \autoref{fig:cu_xs}?}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/47Sc_fixed.pdf}
 % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
 \caption{Measured \ce{^{47}Ti}(n,p)\ce{^{47}Sc} relative production cross section.}
 \label{fig:sc_xs}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
 % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
 \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} relative production cross section}
 \label{fig:cu_xs}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/64cu_fixed_zoom.pdf}
 % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
 \caption{A zoomed-in view of \autoref{fig:cu_xs}.}
 \label{fig:cu_xs_zoom}
\end{figure}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Results of cross section measurement. Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
\label{tab:xs_results}
\begin{tabular}{@{}cc@{}}
\toprule
Reaction                                                                            & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                       \\ \midrule
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX *\end{tabular}                   \\ \bottomrule
\end{tabular}
\end{table}

@@

Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \textcolor{red}{[XXXXref original experimental papers]}. The weighted average of our measurements give \textcolor{red}{XXXXXX} for \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \textcolor{red}{YYYYYY} for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}. The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textcolor{red}{6\%}). However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the \textcolor{red}{XXX groups} and both the ENDF/B-VII.1\textcolor{red}{[XXXref citation]} and TALYS\textcolor{red}{[XXXref citation]} values, but significantly below the results from \textcolor{red}{YYY}.

\comment{fill in missing data, verify \% uncertainty, fill in missing group names, verify ENDF/B-VII.1 as latest}

% \cite{koning2005talys}.

\comment{Also make sure to cite the original experimental work either here, or later when you review the values we determined.}

\comment{Add Shimizu data into plots , as well as 115In capture points}

\comment{Change to zoomed-in view like in \autoref{fig:cu_xs} as appropriate}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/47Sc_fixed.pdf}
 % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
 \caption{Measured \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section relative to indium activation.}
 \label{fig:sc_xs}
\end{figure}

% \begin{figure}
%  \centering
%  \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
%  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
%  \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} relative production cross section}
%  \label{fig:cu_xs}
% \end{figure}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/64cu_fixed_zoom.pdf}
 % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
 \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section relative to indium activation.}
 \label{fig:cu_xs_zoom}
\end{figure}

As mentioned above, the cross section can be obtained relative to both the inelastic scattering cross sections on \ce{^{113}In} and \ce{^{115}In}, and the capture of fast, unmoderated neutrons on \ce{^{115}In}.  The results from both are consistent, indicating that the contributions from thermal \enquote{room return} neutrons are negligible for samples mounted in the center of the HFNG.  This builds confidence in our results, and highlights the potential of using the HFNG for fast neutron capture reactions via activation.  This will be discussed in greater detail in the conclusion section below.

\comment{verify this claim!}
